\section{Future Challenges}
\label{futurework}

Before our work can be useful in real HPC deployments, we need to address
several challenges.

First, we will layer our middleware on top of a real cluster file system.
This will allow us to inherit the data path scalability when accessing the 
file data as well as \ldb's SSTables. We also plan to explore how
we can effectively leverage the fault tolerance mechanisms and system
configuration tools already present in the cluster file systems.

Second, we will minimize the FUSE overheads associated with accessing files.
Even after the application gets a symbolic link pointing to the physical
location of the file, our current prototype will rely of FUSE and VFS to
dereference the symbolic link. We want to avoid this FUSE
interposition by changing the FUSE kernel module to support distributed file
system file handles but still receive prompt notifications of attribute changes
on file close.

Third, we will explore several recently published optimizations to minimize the
background compaction operations triggered by data stores built on the LSM
trees and similar data-structures \cite{blsm, tokufs, Bender2007}. 
While compactions is a necessary evil: in order to speed up future reads and
scans, the steal resources from foreground operations that happen
simultaneously with these background operations.

\section{Summary}
\label{summary}

Modern cluster file systems provide highly scalable I/O bandwidth along the
data path by enabling highly parallel access to file data.
Unfortunately metadata scaling is lagging behind data scaling.
We propose a file system design that 
inherits the scalable data bandwidth of existing cluster file systems
and adds support for distributed and high-performance metadata operations.
Our idea is to integrate a distributed indexing mechanism with general-purpose
optimized on-disk metadata store.
Early prototype evaluation shows that our approach outperforms popular Linux
local file systems and scales well with large numbers of file creations. 

%inherits data bandwidth and adds the metadata bandwidth scaling

%split and migrate without moving the underlying objects


